Network based multifactorial modelling microRNA-target interaction.

### 2019-12-20 NAR_form_article.Rmd
Adding discussion final part and selcen's name

---
title: Network based multifactorial modelling microRNA-target interaction.
author:
  - name: Selcen Ari
    affiliation: "1"
  - name: Alper Yilmaz
    affiliation: "1"
    correspond: "To whom correspondence should be addressed. Phone: +90 212 383 4627 Fax: +90 212 383 4625  Email: alyilmaz@yildiz.edu.tr"
    separator: "and"
address:
  - code: 1
    address: Department of Bioengineering, Yildiz Technical University, Istanbul, Turkey

@@

>>>>

---
title: Network based multifactorial modelling microRNA-target interaction.
author:
  - name: Selcen Ari Yuka
    affiliation: "1"
  - name: Alper Yilmaz
    affiliation: "1"
    correspond: "To whom correspondence should be addressed. Phone: +90 212 383 4627 Fax: +90 212 383 4625  Email: alyilmaz@yildiz.edu.tr"
    separator: "and"
address:
  - code: 1
    address: Department of Bioengineering, Yildiz Technical University, Istanbul, Turkey

@@

In breast cancer sample, all the genes with high perturbation efficiency were found to be all connected to miR10b. This can be explained by very high expression level of that miRNA. In a large network where miRNAs have balanced expression, perturbation analysis have potential to reveal genes with high perturbation efficiency more widsespread and dispersed in the network.
